Popularity, Mixed Matchings, and Self-duality

### 2017-04-03 CO750-ApproximationAlgorithmsTopics/assignments/assignment_03.tex
trying 2b

\item Output the set $\bar{L} \subseteq L$ such that $\ell \in \bar{L}$ iff there exists an arc in $R$ that correponds to $\ell$.

@@

For each $\ell \in L^*$ add the arcs which correspoind to $\ell$ to $R^*$. Now we have $c(L^*) = 2c(R^*)$. It remains to fix connectivity in $R^*$ so that there is a directed path from $r$ to each vertex. We will fix it by adding $0$ cost arcs. For each $u \in V\backslash \{r\}$ do the following. Let $p$ be the parent of $u$ with respect to the orientation of step $1$.  Let $G_u$ be the connected component of $G-up$ which contains $u$ and let $G_p$ be the connected component of $G-up$ which contains $p$. Since $L^*$ is feasible for $(WTAP)$ there exists some $ab \in L^*$ such that $a \in V(G_u)$ and $b \in V(G_p)$. Now $a$ is a descendant of $u$. Thus there exists a $0$-cost directed path from $a$ to $u$. Add this path to $R^*$. Note this does not change $c(R^*)$.

@@

Now we change $(WTAP)$ so that the requirement is $(V, E\cup \bar{L})$ is $2$-vertex-connected.

>>>>

\item Output the set $\bar{L} \subseteq L$ such that $\ell \in \bar{L}$ iff there exists an arc in $R$ that corresponds to $\ell$.

@@

For each $\ell \in L^*$ add the arcs which correspond to $\ell$ to $R^*$. Now we have $c(L^*) = 2c(R^*)$. It remains to fix connectivity in $R^*$ so that there is a directed path from $r$ to each vertex. We will fix it by adding $0$ cost arcs. For each $u \in V\backslash \{r\}$ do the following. Let $p$ be the parent of $u$ with respect to the orientation of step $1$.  Let $G_u$ be the connected component of $G-up$ which contains $u$ and let $G_p$ be the connected component of $G-up$ which contains $p$. Since $L^*$ is feasible for $(WTAP)$ there exists some $ab \in L^*$ such that $a \in V(G_u)$ and $b \in V(G_p)$. Now $a$ is a descendant of $u$. Thus there exists a $0$-cost directed path from $a$ to $u$. Add this path to $R^*$. Note this does not change $c(R^*)$.

@@

Now we change $(WTAP)$ so that the requirement is $(V, E\cup \bar{L})$ is $2$-vertex-connected. Since links between adjacent vertices do not help $2$-vertex-connectivity we may assume there are no such links, otherwise just discard them before starting the algorithm. We will modify the algorithm $\cA$ as follows, the big changes are that we take a leaf to be the root, and we ``shorten" the downward arcs:
\item Select an arbitrary leaf $r \in V$ as the root. Orient $E$ towards $r$, and set the $w(a) = 0$ for all the resulting arcs $a$.
	\item For each downward arc $(p,u)$ do: if $p$ is not a leaf let $c_p$ be the child of $p$  that succeeds $p$ on the path to $u$ (otherwise let $c_p = p$). If $u$ is not a leaf let $p_u$ be the parent of $u$ (otherwise let $p_u = u$). Replace the arc $(p,u)$ with the arc $(c_p, p_u)$ with the same weight, and same corresponding link as $(p,u)$.
\item Output the set $\bar{L} \subseteq L$ such that $\ell \in \bar{L}$ iff there exists an arc in $R$ that corresponds to $\ell$.
\begin{lemma}\label{lemma:3b-poly}
As argued in lemma \ref{lemma:3a-poly} the algorithm $\cA$ runs in polynomial time, it is clear that the additional processing runs in polynomial time. To verify feasibility suppose for a contradiction that the graph $H := (V, E \cup \bar{L})$ has a vertex $p$ whose deletion disconnects the graph. Let $g$ be the parent of $p$. The vertex $g$ exists since we choose $r$ to be a leaf and hence $p \neq r$. Let $u_1, \dots, u_k$ be the children of $p$. For each $v \in V$, let $C(v)$ denote the connected component of $H-p$ containing vertex $v$. Let $A := \{u \in \{u_1, \dots, u_k\} : u \in C(g)\}$ be the set of children of $p$ which are connected to $g$ after removing $p$. We claim that $A \neq \emptyset$.
Clearly $r \in C(g)$, as are all ancestors of $p$. Now since $R$ is an $out$-arborescence there exists a directed path from $r$ to $p \cup \bigcup_{i=1}^k u_i$. The arc such a path uses to enter $p \cup \bigcup_{i=1}^k u_i$ is a downward arc from some ancestor of $p$, $a$, to either $p$ or a descendant of $p$, $d$. If the arc is of the form $(a,d)$ then the corresponding link connects an ancestor of $p$ to some descendant of a child $u_i$. Hence $C(g)$ is connected to $C(u_i)$. That is $u_i \in A$ and hence $A \neq \emptyset$. In the case the arc is of the form $(a,p)$, then by our construction of $(a,p)$ in step $2(b)$ there is a link in $\bar{L}$ connecting an ancestor of $p$ to some child of $p$, $u_i$. Thus $C(g)$ is connected to $C(u_i)$. Therefore our claim that $A$ is not empty holds. Let $\bar{A} = \{u_1, \dots, u_k\} \backslash A$. By our contradiction assumption, $\bar{A}\neq \emptyset$ as otherwise removing $p$ does not disconnect $H$.
Now, again since $R$ is an $out$-arborescence there exists a directed path from $r$ to $\bigcup_{u \in \bar{A}} C(u)$. The directed arc which enters $\bigcup_{u \in \bar{A}} C(u)$ is either a downward ar 
